\thispagestyle{empty}
% Half-Title Page.

\NewFontFamily\mont{Mont}
\vspace*{6\nbs}
\begin{center}
{\mont \charscale[2]{SUBCUTANEAN}}
\end{center}
\clearpage

\thispagestyle{empty}
\null % Necessary for blank page.
% Alternatively, List of Books.
\clearpage

\thispagestyle{empty}
% Title Page.
% Use different font
\vspace*{6\nbs}
\begin{center}
{\mont \charscale[2]{SUBCUTANEAN}}

\vspace*{3\nbs}

{\mont \charscale[1.25]{by Aaron A. Reed}}

\vfill
Printed in the United States of America by TheBookPatch.com

\end{center}
\clearpage

\thispagestyle{empty}
% Copyright Page.
\null\vfill
% legalese environment?

\begin{legalese}
Typeset in LaTeX using the \textit{novel} class by Robert Allgeyer, the NovelDeco and Mont fonts, and custom code by the author. \\
\vspace{1\nbs}
ARC Edition, 2019 \\
% First Edition(s), 2020
\vspace{1\nbs}
SEED_TEXT \\

\vspace{1\nbs}

\begin{parascale}[0.88]
Seed Number Key: \\
\begin{adjustwidth}{2em}{2em}
Seeds starting with 0: Advance Reader Copies \\
Seeds starting with 1: Limited Crowdfunder Editions \\
Seeds starting with 2: Launch Editions, 2020
\end{adjustwidth}
\end{parascale}
\vspace{1\nbs}

Copyright 2019 Aaron A. Reed.
\end{legalese}
\clearpage

\thispagestyle{empty}
% Dedication or Epigraph or TOC or Acknowledgements or Author's Note or Map.
% Alternatively, repeat the Half-Title.

\vspace*{10\nbs}

\begin{adjustwidth}{4em}{4em}
\begin{parascale}[0.88]
The book you're holding is unique. There is no other exactly like it.

Each printing of \textsc{Subcutanean} is different. This is the one and only version generated from seed SEED_NUMBER. Words, sentences, or whole scenes may appear in this printing but not in others, or vice versa. No two copies are alike.

But all of them are the same story, more or less. Don't worry about what's in the other versions. It doesn't matter. This is the one that's happening to you.

This is the one you have.  

% This is a special Advance Reader Copy of \textsc{Subcutanean}. In the final version, each printing of the book will be unique, generated from a specific seed. Words, sentences, or whole scenes may appear in some printings but not in others, or vice versa. No two copies will be alike.

% For now, each Advance Reader Copy in this printing shares the seed SEED_NUMBER, and the same text.


% This is the one that has you.
\end{parascale}
\end{adjustwidth}

\vspace*{2\nbs}

\begin{center}
\textsc{subcutanean.textories.com}
\end{center}

\clearpage
% \cleartorecto


